Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-08 prop.tex
prob.tex \section{Conclusion and Discussion} Updating...

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. Despite the fact that classically a interval-valued
probability measure could always correspond to a real-valued probability
measure, we found that there may be no ``real'' infinitely-precise
quantum state approximated by a quantum interval-valued probability
measure as a whole. However, if a quantum interval-valued probability
measure is decomposed into pieces, each piece might still be induced
by a quantum state. Moreover, our examples and Gleason's theorem summarized
in table~\ref{table_long} suggests that as the measurement resources
increase, an entire quantum interval-valued probability measure could
more and more likely be identified to a particular state. 
\begin{table}[ht]
\center{%
\begin{tabular}{c|cccc}
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\hline 
Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\hline 
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
measures}
\label{table_long}
\end{table}
Additional work is in progress on the following research questions:
\begin{description}
\item [{Research Question.}] Confirm that there is always a quantum interval-valued
probability measure with an empty-core if the length of the intervals
is bigger than zero. 
\item [{Research Question.}] Find a general method to determine how a
quantum interval-valued probability measure is close to the Born rule. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum interval-valued probability
measure converges to the measure induced by the Born rule. 
\item [{Research Question.}] Investigate the status of the theorems of
Gleason, Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker for quantum interval-valued probability measures.
\end{description}
Although we discussed how a quantum interval-valued probability measure
could be induced from a real quantum state, our investigation leaves
an open question of whether there exists a ``real'' entity that
exists independently of measurements and probabilities. This idea
is consistent with the elegantly recent work on Quantum Bayesianism
or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which suggests
that the quantum state is more like an interactive system in computer
science parlance. Moreover, the quantum state is subjective: each
observer has a different view of the quantum system that is consistent
with their previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.

>>>>

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. Despite the fact that classically a interval-valued
probability measure could always correspond to a real-valued probability
measure, we found that there may be no ``real'' infinitely-precise
quantum state approximated by a quantum interval-valued probability
measure as a whole. However, if a quantum interval-valued probability
measure is decomposed into pieces, each piece might still be induced
by a quantum state. Moreover, our examples and Gleason's theorem summarized
in table~\ref{table_long} suggests that as the measurement resources
increase, an entire quantum interval-valued probability measure could
more and more likely be identified to a particular state. 
\begin{table}[ht]
\center{%
\begin{tabular}{c|cccc}
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\hline 
Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\hline 
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
measures}
\label{table_long}
\end{table}
Additional work is in progress on the following research questions:
\begin{description}
\item [{Research Question.}] Confirm that there is always a quantum interval-valued
probability measure with an empty-core if the length of the intervals
is bigger than zero. 
\item [{Research Question.}] Find a general method to determine how a
quantum interval-valued probability measure is close to the Born rule. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum interval-valued probability
measure converges to the measure induced by the Born rule. 
\item [{Research Question.}] Investigate the status of the theorems of
Gleason, Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker for quantum interval-valued probability measures.
\end{description}
Although we discussed how a quantum interval-valued probability measure
could be induced from a real quantum state, our investigation leaves
an open question of whether there exists a ``real'' entity that
exists independently of measurements and probabilities. The possibility
of no ``real'' underlying state is consistent with the elegantly
recent work on Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
which suggests that the quantum state is more like an interactive
system in computer science parlance. In another word, the quantum
state is subjective: each observer has a different view of the quantum
system that is consistent with their previous observations and that
allows that observer, independently of other observers, to assign
beliefs (i.e., probabilities) to possible future interactions.
